---
title: "memo"
author: "Aoi Ogawa, Stella"
date: "3/23/2018"
output: html_document
---

```{r}
# #make function
# 
#   
# contribution_party <- function(name_arg) {
#   
# all_party <- party_contribution %>%
#   filter(cand_party_affiliation == name_arg)
# 
# 
# 
# mapping <- ggplot(all_party, aes(map_id = cand_state)) + 
#   # map points to the fifty_states shape data
#   geom_map(aes(fill = contri_party), map = fifty_states) + 
#   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
#   coord_map() +
#   scale_x_continuous(breaks = NULL) + 
#   scale_y_continuous(breaks = NULL) +
#   labs(x = "", y = "", title = name_arg) +
#   theme(legend.position = "bottom", 
#         panel.background = element_blank()) + labs(fill = "Amount of Contribution") 
# 
# 
# }
# 
# #
# #+ geom_text(data = fifty_statesaes(x = long, y = fifty_states$lat, label = state)) + geom_text(data= sum_data, alpha = 1, color = "black") + scale_fill_continuous( low = "#B0E2FF", high = "#607B8B")
# 
# party_plots <- lapply(parties, contribution_party)
# 
# party_plots
```


#mapping if there is more R winning than D the map turns red and the other way it is blue

# mapping <- ggplot(all_party, aes(map_id = cand_state)) + 
#   # map points to the fifty_states shape data
#   geom_map(aes(fill = contri_party), map = fifty_states) + 
#   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
#   coord_map() +
#   scale_x_continuous(breaks = NULL) + 
#   scale_y_continuous(breaks = NULL) +
#   labs(x = "", y = "", title = name_arg) +
#   theme(legend.position = "bottom", 
#         panel.background = element_blank()) + labs(fill = "Amount of Contribution") 
-------------------------------------------------------------------






```{r}
# mapping <- ggplot(party_contribution, aes(map_id = cand_state)) +
#   # map points to the fifty_states shape data
#   geom_map(aes(fill = contri_party), map = fifty_states) +
#   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
#   coord_map() +
#   scale_x_continuous(breaks = NULL) +
#   scale_y_continuous(breaks = NULL) +
#   labs(x = "", y = "") +
#   theme(legend.position = "bottom",
#         panel.background = element_blank()) + labs(fill = "Amount of Contribution") + facet_wrap(~ cand_party_affiliation) + scale_fill_continuous(breaks = c(-1000, 214500,429046963), labels = c("-1k","214500K", "429000K"),low = "#B0E2FF", high = "#607B8B") + geom_text(aes(x = fifty_states$long, y = fifty_states$lat, label = state), data= sum_data, alpha = 1, color = "black")
# 
# mapping

```
# 
# # add border boxes to AK/HI
# #mapping + fifty_states_inset_boxes()
# # ggplot(party_contribution, aes(x = cand_party_affiliation, y = contri_party)) + geom_bar(stat = "identity") + facet_wrap(~state)

```





-------------------------------------------------------------------


```{r, message=FALSE, warning=FALSE}

# sum of general votes per state
sum_vote<- house_elections %>%
  group_by(state) %>%
  summarise(sum_vote = sum(general_votes)) %>%
  filter(state %in% fifty_states_name)


# sum of contribution for each state
sum_contribution <- contributions %>% 
  group_by(state) %>%
  summarise(sum_contribution = sum(transaction_amt))

sum_data <- inner_join(sum_vote, sum_contribution)
```


```{r,message=FALSE, warning=FALSE}
# changing the the observation name in the sum_data data frame
sum_data$state[sum_data$state== "AK"] <- "alaska"
sum_data$state[sum_data$state== "AL"] <- "alabama"
sum_data$state[sum_data$state== "AR"] <- "arkansas"
sum_data$state[sum_data$state== "AZ"] <- "arizona"
sum_data$state[sum_data$state== "CA"] <- "california"
sum_data$state[sum_data$state== "CO"] <- "colorado"
sum_data$state[sum_data$state== "CT"] <- "connecticut"
sum_data$state[sum_data$state== "DE"] <- "delaware"
sum_data$state[sum_data$state== "FL"] <- "florida"
sum_data$state[sum_data$state== "GA"] <- "georgia"
sum_data$state[sum_data$state== "HI"] <- "hawaii"
sum_data$state[sum_data$state== "IA"] <- "iowa"
sum_data$state[sum_data$state== "ID"] <- "idaho"
sum_data$state[sum_data$state== "IL"] <- "illinois"
sum_data$state[sum_data$state== "IN"] <- "indiana"
sum_data$state[sum_data$state== "KS"] <- "kansas"
sum_data$state[sum_data$state== "KY"] <- "kentucky"
sum_data$state[sum_data$state== "LA"] <- "louisiana"
sum_data$state[sum_data$state== "MA"] <- "massachusetts"
sum_data$state[sum_data$state== "MD"] <- "maryland"
sum_data$state[sum_data$state== "ME"] <- "maine"
sum_data$state[sum_data$state== "MI"] <- "michigan"
sum_data$state[sum_data$state== "MN"] <- "minnesota"
sum_data$state[sum_data$state== "MO"] <- "missouri"
sum_data$state[sum_data$state== "MS"] <- "mississippi"
sum_data$state[sum_data$state== "MT"] <- "montana"
sum_data$state[sum_data$state== "NC"] <- "north carolina"
sum_data$state[sum_data$state== "ND"] <- "north dakota"
sum_data$state[sum_data$state== "NE"] <- "nebraska"
sum_data$state[sum_data$state== "NH"] <- "new hampshire"
sum_data$state[sum_data$state== "NJ"] <- "new jersey"
sum_data$state[sum_data$state== "NM"] <- "new mexico"
sum_data$state[sum_data$state== "NV"] <- "nevada"
sum_data$state[sum_data$state== "NY"] <- "new york"
sum_data$state[sum_data$state== "OH"] <- "ohio"
sum_data$state[sum_data$state== "OK"] <- "oklahoma"
sum_data$state[sum_data$state== "OR"] <- "oregon"
sum_data$state[sum_data$state== "PA"] <- "pennsylvania"
sum_data$state[sum_data$state== "RI"] <- "rhode island"
sum_data$state[sum_data$state== "SC"] <- "south carolina"
sum_data$state[sum_data$state== "SD"] <- "south dakota"
sum_data$state[sum_data$state== "TN"] <- "tennessee"
sum_data$state[sum_data$state== "TX"] <- "texas"
sum_data$state[sum_data$state== "UT"] <- "utah"
sum_data$state[sum_data$state== "VA"] <- "virginia"
sum_data$state[sum_data$state== "VT"] <- "vermont"
sum_data$state[sum_data$state== "WA"] <- "washington"
sum_data$state[sum_data$state== "WI"] <- "wisconsin"
sum_data$state[sum_data$state== "WV"] <- "west virginia"
sum_data$state[sum_data$state== "WY"] <- "wyoming"

```




```{r, message=FALSE, warning=FALSE}
# all_contributions <- contributions %>% 
#   group_by(cand_id) %>%
#   summarize(contribution_sum = sum(transaction_amt)) 
# 
# condi_contri <- house_elections %>% left_join(all_contributions, by = "cand_id")
```


```{r, message=FALSE, warning=FALSE}
# #The contributors ranking from the most contributor to the least 
# most_contri <- contributions %>%
#   group_by(cmte_id) %>%
#   summarise(sum_trans = sum(transaction_amt)) %>%
#   arrange(desc(sum_trans))
# 
# most_can <- contributions %>%
#   group_by(cmte_id) %>%
#   summarise(sum_can = sum(n_distinct(cand_id))) %>%
#   arrange(desc(sum_can))
# 
# # the data set which describes the most contribution and how many candidates the contributors are supporting 
# money_n_ppl <- inner_join (most_contri, most_can) 
# 
# # Looking at the contributor (top 10) and the candidates elecition results
# top_10_contributors <- money_n_ppl %>%
#   head(10)
# 
# top_10 <- top_10_contributors$cmte_id
# 
# 
# 
# top_10_candi <- contributions %>%
#   filter(cmte_id %in% top_10)
# 
# 
# data_sum <- contributions %>% inner_join (house_elections, by = "cand_id")

```


```{r, message=FALSE, warning=FALSE}
# # which contributors supported the most elected candidates 
# winner_num <- data_sum %>%
#   filter(winner == "1") %>%
#   group_by(cmte_id) %>%
#   summarise(sum_win = sum(n_distinct(cand_id)))
#   
# 
# # %>% 
# #   group_by(cmte_id) %>%
# #   summarise(n_winner = sum(n_distinct(winner)))
# 
# # the sum of candidates who the contributor is suporting 
# all_sum <- data_sum %>%
#   group_by(cmte_id) %>%
#   summarise(sum_can = sum(n_distinct(cand_id)))
# 
# # the sum of candidates who has been elected
# rate_elected <- inner_join(winner_num, all_sum) %>%
#   mutate(rate = sum_win/sum_can) %>%
#   arrange(desc(sum_win)) %>%
#   arrange(desc(rate)) 
#   
# 
# # a data set that contains the rate of winning the election and the amount of contribution 
# sum_contri <- inner_join(rate_elected, most_contri)
# # => there's no relationship between contribution and the rate of the person who will get elected 
```

```{r, message=FALSE, warning=FALSE}
# sum_contri %>% filter(sum_win > 20)
```


```{r, message=FALSE, warning=FALSE}
# all_contributions <- contributions %>% 
#   group_by(cand_id) %>%
#   summarize(contribuion_sum = sum(transaction_amt)) 
#   
# candidates_n_contributions <- inner_join(candidates, contributions)
# 
# house_elections <- house_elections %>%
#   rename(cand_id = fec_id)
# 
# candidates_n_contributions %>% left_join(house_elections, by = "cand_id")
```


```{r, message=FALSE, warning=FALSE}
# # Mapping
# 
# 
# # data("fifty_states") # this line is optional due to lazy data loading
# # 
# crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
# # 
# # # map_id creates the aesthetic mapping to the state name column in your data
# # p <- ggplot(crimes, aes(map_id = state)) + 
# #   # map points to the fifty_states shape data
# #   geom_map(aes(fill = Assault), map = fifty_states) + 
# #   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
# #   coord_map() +
# #   scale_x_continuous(breaks = NULL) + 
# #   scale_y_continuous(breaks = NULL) +
# #   labs(x = "", y = "") +
# #   theme(legend.position = "bottom", 
# #         panel.background = element_blank())
# # 
# # p
# # # add border boxes to AK/HI
# # p + fifty_states_inset_boxes() 
# 
# ```

```{r, message=FALSE, warning=FALSE}
# data("fifty_states") # this line is optional due to lazy data loading
# 
# # map_id creates the aesthetic mapping to the state name column in your data
# mapping <- ggplot(sum_data, aes(map_id = state)) + 
#   # map points to the fifty_states shape data
#   geom_map(aes(fill = sum_vote), map = fifty_states) + 
#   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
#   coord_map() +
#   scale_x_continuous(breaks = NULL) + 
#   scale_y_continuous(breaks = NULL) +
#   labs(x = "", y = "") +
#   theme(legend.position = "bottom", 
#         panel.background = element_blank()) + labs(fill = "Number of Votes") + scale_fill_continuous(breaks = c(250000, 6270000,12204357), labels = c("240k","6270K", "12300K"),low = "#9BF5FF", high = "#53868B")
#   
# # add border boxes to AK/HI
# mapping + fifty_states_inset_boxes()

#not include VI(virfin islands), PR(Puerto Rico), MP(northern Mariana Islands), GU (Guam), DC(district of columbia), AS(?)
```


- contribution sum of the states 
```{r, message=FALSE, warning=FALSE}
mapping <- ggplot(sum_data, aes(map_id = state)) +
  # map points to the fifty_states shape data
  geom_map(aes(fill = sum_contribution), map = fifty_states) +
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "") +
  theme(legend.position = "bottom",
        panel.background = element_blank()) + labs(fill = "Amount of Contribution") + scale_fill_continuous(breaks = c(1170000, 214200000,425544900), labels = c("240k","214200K", "426000K"),low = "#B0E2FF", high = "#607B8B")

# + geom_text(aes(x = fifty_states$long, y = fifty_states$lat, label = state), data= sum_data, alpha = 1, color = "black")


# add border boxes to AK/HI
mapping + fifty_states_inset_boxes()
```

```{r}
# # votes per state per party
# party_votes <- house_elections %>%
#   filter(state %in% fifty_states)
# 
# # %>%
# #   group_by(state, party) %>%
# #   summarise(vote_party = sum(general_votes)) 
#   
# 
# ggplot(party_votes, aes(x = party, y = vote_party)) + geom_bar(stat = "identity") + facet_wrap(~state)
```
