---
title: "Mini-Project 2"
author: "Aoi and Stella"
date: "March 9, 2018"
output: html_document
---


## Loading the data

This project is so interesting and relevant to my life!

```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
library(tidyverse)
library(dplyr)

```

The data set is from 2011-2012.
canditates = Candidate Master File
committees = Committee Master File
contributions = Contributions to Candidates (and other expenditures) from committees

idea

- is there a relaitonship between amount of contribution and being elected?

- which contributor is contributing the most? and is there a contributor which tends to contribute to the winner? and the relation with the transaction type ==> use candidate ids to link to the candidates  

- How different are men and women candidates in general? the amount of contribution, the amount of voting, and the rate of being elected 

```{r}
house_elections <- house_elections %>%
  mutate(winner = ifelse(ge_winner == "W", 1, 0)) 
house_elections$"ifelse(ge_winner == \"W\", 1, 0)"<- NULL
house_elections$"winner <- ifelse(ge_winner == \"W\", 1, 0)"<- NULL
```


```{r}
all_contributions <- contributions %>% 
  group_by(cand_id) %>%
  summarize(contribuion_sum = sum(transaction_amt)) 
  
candidates_n_contributions <- inner_join(candidates, contributions)

house_elections <- house_elections %>%
  rename(cand_id = fec_id)

candidates_n_contributions %>% left_join(house_elections, by = "cand_id")
```

<<<<<<< HEAD
=======
```{r}
all_contributions <- contributions %>% 
  group_by(cand_id) %>%
  summarize(contribuion_sum = sum(transaction_amt)) 

house_elections <- house_elections %>%
  rename(cand_id = fec_id)

condi_contri <- left_join(house_elections, all_contributions)
```
>>>>>>> 1aa539b7388934b75252cd1e3589d01fddc7d6e5

